\begin{longtable}[H]{p{0.25\textwidth}|p{0.555\textwidth}|p{0.145\textwidth}|p{0.05\textwidth}}
\caption{\textbf{Sélection de trois articles emblématiques pour chacun des sujets associés à la supersymétrie}. Les articles sont sélectionnés parmi ceux qui mentionnent la supersymétrie dans leur résumé.}
\label{table:emblematic_articles}\\
\toprule
                                                                    &                                                                      &   Catégories & $\theta_{z}$ \\
Sujet & Article &              &              \\
\midrule
\endfirsthead
\caption[]{\textbf{Sélection de trois articles emblématiques pour chacun des sujets associés à la supersymétrie}. Les articles sont sélectionnés parmi ceux qui mentionnent la supersymétrie dans leur résumé.} \\
\toprule
                                                                    &                                                                      &   Catégories & $\theta_{z}$ \\
Sujet & Article &              &              \\
\midrule
\endhead
\midrule
\multicolumn{4}{r}{{Suite page suivante}} \\
\midrule
\endfoot

\bottomrule
\endlastfoot
\multirow{3}{*}{\begin{tabular}{l}Théories de\\ jauge supersymé\\ triques\end{tabular}} & ``N=4 superparticle and super Yang-Mills theory in USp(4) harmonic superspace'' &      Théorie &         0.30 \\
                                                                    & ``Supersymmetric U(N) gauge model and partial breaking of N=2 supersymmetry'' &      Théorie &         0.25 \\
                                                                    & ``Superspace Formulation of Ten-dimensional $N=1$ Supergravity Coupled to $N=1$ Superyang-mills Theory'' &      Théorie &         0.23 \\
\cline{1-4}
\multirow{3}{*}{\begin{tabular}{l}Super-algèbres\\ et super-champs\end{tabular}} & ``Evidence for the classical integrability of the complete $AdS_4 x CP^3$ superstring'' &      Théorie &         0.30 \\
                                                                    & ``Supersymmetric nonlinear sigma models'' &      Théorie &         0.27 \\
                                                                    & ``THE N=2 SUPER KAC-MOODY ALGEBRA AND THE WZW MODEL IN (2,0) SUPERSPACE'' &      Théorie &         0.26 \\
\cline{1-4}
\multirow{3}{*}{\begin{tabular}{l}Higgs au-delà\\ du Modèle\\ Standard\end{tabular}} & ``Supersymmetric electroweak symmetry breaking'' &       Phéno. &         0.24 \\
                                                                    & ``Radiative natural SUSY with a 125 GeV Higgs boson'' &       Phéno. &         0.22 \\
                                                                    & ``The Higgs sector of the next-to-minimal supersymmetric standard model'' &       Phéno. &         0.22 \\
\cline{1-4}
\multirow{3}{*}{\begin{tabular}{l}Supergravité\end{tabular}} & ``Brane superpotential and local Calabi-Yau manifolds'' &      Théorie &         0.27 \\
                                                                    & ``Consistent Kaluza-Klein reductions for general supersymmetric AdS solutions'' &      Théorie &         0.24 \\
                                                                    & ``On toric geometry, spin(7) manifolds, and type two superstring compactifications'' &      Théorie &         0.24 \\
\cline{1-4}
\multirow{3}{*}{\begin{tabular}{l}Boson de Higgs\end{tabular}} & ``Search for Higgs bosons of the minimal supersymmetric standard model in $p\bar{p}$ collisions at $\sqrt{s}=1.96$ TeV'' &  Exp./Phéno. &         0.27 \\
                                                                    & ``Heavy Z Boson Decays to W, Z and Higgs Bosons in E(6) Superstring Models'' &         Exp. &         0.27 \\
                                                                    & ``The Lightest neutral and doubly charged Higgs bosons of supersymmetric left-right models'' &       Phéno. &         0.25 \\
\cline{1-4}
\multirow{3}{*}{\begin{tabular}{l}Phénoménologie\\ de la\\ supersymétrie\\ et superpartena\\ ires\end{tabular}} & ``Long-lived bino and wino in supersymmetry with heavy scalars and higgsinos'' &  Exp./Phéno. &         0.28 \\
                                                                    & ``Predicting Supersymmetry'' &       Phéno. &         0.25 \\
                                                                    & ``Gaugino Anomaly Mediated SUSY Breaking: phenomenology and prospects for the LHC'' &       Phéno. &         0.23 \\
\cline{1-4}
\multirow{3}{*}{\begin{tabular}{l}Leptons et\\ physique de la\\ saveur\end{tabular}} & ``Search for lepton flavor violation in supersymmetric models via meson decays'' &       Phéno. &         0.17 \\
                                                                    & ``Enhanced lepton flavor violation in the supersymmetric inverse seesaw model'' &       Phéno. &         0.16 \\
                                                                    & ``Supersymmetric lepton flavor violation at e+ e- linear colliders'' &       Phéno. &         0.16 \\
\end{longtable}
